Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-27 paper.tex
add 2025 article

\subsection{Case study: Our Future Health genotype data}
Our Future Health~\cite{ofhmain_2025}  is the UK’s largest ever health research programme.
It is designed to help people live healthier lives for longer through the
discovery and testing of more effective approaches to prevention, earlier
detection and treatment of diseases.
Our Future Health is inviting millions of people, from all backgrounds and
from right across the UK to take part. Volunteers are providing information
about their health and lifestyles to create an incredibly detailed picture
that represents the whole of the UK.

>>>>

\subsection{Case study: Our Future Health genotype data}
Our Future Health~\cite{ofhmain_2025, Cook2025}  is the UK’s largest ever health research programme.
It is designed to help people live healthier lives for longer through the
discovery and testing of more effective approaches to prevention, earlier
detection and treatment of diseases.
Our Future Health is inviting millions of people, from all backgrounds and
from right across the UK to take part. Volunteers are providing information
about their health and lifestyles to create an incredibly detailed picture
that represents the whole of the UK.
